20220416_descriptives

### 2022-04-17 exploratory/20220416_descriptives.Rmd
finished the exploratory analyses, close #4

---
title: "20220416_descriptives"
author: "Yurun (Ellen) Ying"
date: "4/16/2022"
output: github_document

@@

# read file
casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
  read_csv()
```

@@

- number of men and women who were in the mating pool `m_inpool` `f_inpool`
- number of men and women who were out of the mating pool `m_outpool` ` f_outpool`
- average number of short-term mating experiences of total populations of men and women `m_exp_all` `f_exp_all`
- average number of short-term mating experiences of men and women in the pool `m_exp_ip` `f_exp_ip`
- average number of short-term partners of total populations of men and women `m_partner_all` `f_partner_all`
- average number of short-term partners of men and women in the pool `m_partner_ip` `f_partner_ip`

@@

### Distributions of the outcome variables
- Number of men and women in the mating pool
```{r e1_inpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_inpool, f_inpool) %>% 
  pivot_longer(m_inpool:f_inpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Heterosexual Men and\nWomen in the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of men and women in the mating pool
```{r e1_exp_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_exp_ip, f_exp_ip) %>% 
  pivot_longer(m_exp_ip:f_exp_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of In-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of men and women in the mating pool
```{r e1_partner_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_ip, f_partner_ip) %>% 
  pivot_longer(m_partner_ip:f_partner_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nIn-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

@@

>>>>

---
title: "20220416_descriptives"
author: "Yurun (Ellen) Ying"
date: "4/16/2022"
output: 
  github_document:
    html_preview: false

@@

# read file
casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
  read_csv() %>% 
  mutate(
    diff_likelihood = as_factor(diff_likelihood),
    diff_standard = as_factor(diff_standard),
    homosexual = as_factor(homosexual)
  )

# add variables for gender differences
casual_tib <- casual_tib %>% 
  mutate(
    diff_inpool = m_inpool - f_inpool,
    diff_outpool = m_outpool - f_outpool,
    diff_exp_all = m_exp_all - f_exp_all,
    diff_exp_ip = m_exp_ip - f_exp_ip,
    diff_partner_all = m_partner_all - f_partner_all,
    diff_partner_ip = m_partner_ip - f_partner_ip
  )
```

@@

- number of men and women who were in the mating pool `m_inpool` `f_inpool`; gender difference `diff_inpool`
- number of men and women who were out of the mating pool `m_outpool` ` f_outpool`; gender difference `diff_outpool`
- average number of short-term mating experiences of total populations of men and women `m_exp_all` `f_exp_all`; gender difference `diff_exp_all`
- average number of short-term mating experiences of men and women in the pool `m_exp_ip` `f_exp_ip`; gender difference `diff_exp_ip`
- average number of short-term partners of total populations of men and women `m_partner_all` `f_partner_all`; gender difference `diff_partner_all`
- average number of short-term partners of men and women in the pool `m_partner_ip` `f_partner_ip`; gender difference `diff_partner_ip`

@@

### Distributions
- Number of heterosexual men and women in the mating pool
```{r e1_inpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_inpool, f_inpool) %>% 
  pivot_longer(m_inpool:f_inpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Heterosexual Men and\nWomen in the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Number of heterosexual men and women out of the mating pool
```{r e1_outpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_outpool, f_outpool) %>% 
  pivot_longer(m_outpool:f_outpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Heterosexual Men and\nWomen out of the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of heterosexual men and women from the whole population
```{r e1_expall_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_exp_all, f_exp_all) %>% 
  pivot_longer(m_exp_all:f_exp_all,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of All Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of heterosexual men and women in the mating pool
```{r e1_expip_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_exp_ip, f_exp_ip) %>% 
  pivot_longer(m_exp_ip:f_exp_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of In-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of heterosexual men and women from the whole population
```{r e1_partnerall_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_all, f_partner_all) %>% 
  pivot_longer(m_partner_all:f_partner_all,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nAll Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of heterosexual men and women in the mating pool
```{r e1_partnerip_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_ip, f_partner_ip) %>% 
  pivot_longer(m_partner_ip:f_partner_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nIn-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

### Gender differences

- Number of heterosexual men and women in the mating pool
```{r e1_inpool_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, diff_inpool) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_inpool, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Number of\nHeterosexual Men and Women in the Mating Pool"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term mating experiences of heterosexual men and women in the mating pool
```{r e1_expip_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, diff_exp_ip) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_exp_ip, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nIn-pool Heterosexual Men and Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term partners of heterosexual men and women in the mating pool
```{r e1_partnerip_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, diff_partner_ip) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_partner_ip, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Partners Among\nIn-pool Heterosexual Men and Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

@@

- **Number of men and women in/out of the mating pool**
  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the number of men and women in/out of the mating pool. 
  - There were more gay men than lesbian women in the mating pool, and less men than women out of the mating pool when there was a gender difference in at least one of the two parameters.
- **Average number of short-term mating experiences of all/in-pool men and women**
  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the average number of short-term mating experiences, regardless of whether the average was taken from the whole population or the in-pool men and women only.
  - Gay men had a higher number of short-term mating experiences than lesbian women on average when there was a gender difference in at least one of the two parameters. This was true regardless of whether the average was taken from the whole population or the in-pool men and women only.
- **Average number of short-term partners of all/in-pool men and women**
  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the average number of short-term partners, regardless of whether the average was taken from the whole population or the in-pool men and women only.
  - Gay men had a higher number of short-term partners than lesbian women on average when there was a gender difference in at least one of the two parameters. This was true regardless of whether the average was taken from the whole population or the in-pool men and women only.

### Distributions 
- Number of gay men and lesbian women in the mating pool
```{r e2_inpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, m_inpool, f_inpool) %>% 
  pivot_longer(m_inpool:f_inpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Gay Men and\nLesbian Women in the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Number of gay men and lesbian women out of the mating pool
```{r e2_outpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, m_outpool, f_outpool) %>% 
  pivot_longer(m_outpool:f_outpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Gay Men and\nLesbian Women out of the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of gay men and lesbian women from the whole population
```{r e2_expall_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, m_exp_all, f_exp_all) %>% 
  pivot_longer(m_exp_all:f_exp_all,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of All Gay Men and Lesbian Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of gay men and lesbian women in the mating pool
```{r e2_expip_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, m_exp_ip, f_exp_ip) %>% 
  pivot_longer(m_exp_ip:f_exp_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of In-pool Gay Men and Lesbian Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of gay men and lesbian women from the whole population
```{r e2_partnerall_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_all, f_partner_all) %>% 
  pivot_longer(m_partner_all:f_partner_all,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nAll Gay Men and Lesbian Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of gay men and lesbian women in the mating pool
```{r e2_partnerip_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_ip, f_partner_ip) %>% 
  pivot_longer(m_partner_ip:f_partner_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nIn-pool Gay Men and Lesbian Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

### Gender differences

- Number of gay men and lesbian women in the mating pool
```{r e2_inpool_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, diff_inpool) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_inpool, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Number of\nGay Men and Lesbian Women in the Mating Pool"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term mating experiences of gay men and lesbian women from the whole population
```{r e2_expall_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, diff_exp_all) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_exp_all, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nAll Gay Men and Lesbian Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term mating experiences of gay men and lesbian women in the mating pool
```{r e2_expip_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, diff_exp_ip) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_exp_ip, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nIn-pool Gay Men and Lesbian Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term partners of gay men and lesbian women from the whole population
```{r e2_partnerall_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, diff_partner_all) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_partner_all, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Parters Among\nAll Gay Men and Lesbian Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```

- Average number of short-term partners of gay men and lesbian women in the mating pool
```{r e2_partnerip_line, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 1) %>% 
  select(diff_likelihood, diff_standard, diff_partner_ip) %>% 
  ggplot(aes(
    x = diff_likelihood, y = diff_partner_ip, group = diff_standard,
    color = diff_standard, fill = diff_standard)) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0.2, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun = mean, geom = "line",
               size = 0.4, linetype = "dashed") +
  scale_x_discrete(
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_fill_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  scale_color_discrete(
    name = "Short-term mating\nstandards",
    labels = c("No gender\ndifference", "Gender\ndifference")) +
  labs(
    x = "Short-term mating likelihood", 
    y = "Gender difference\n(men - women)",
    title = "Gender Difference in the Average Number of\nShort-term Partners Among\nIn-pool Gay Men and Lesbian Women"
       ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    legend.key.height = unit(1.5, units = "lines"))
```
